|

### 2020-03-30 inst/manuscript/candidaev_figures.Rmd
Fix Figure 4C 4D colours
Also, fix minor typos.

```{r table1}
tab1_cap <- "\\textbf{Candidate positive protein markers for 
             \\textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \\textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (ref:footnote1) unless otherwise 
             indicated. The log\\textsubscript{2} ratio of the abundance 
             (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
             whole cell lysate (WCL) for each strain is listed. \`\`ex\" 
             indicates where a protein was only quantified in the EV fraction 
             and not the WCL for that strain. The \`\`TM\" column indicates the 
             number of transmembrane domains for each protein as annotated in 
             UniProt. \`\`SP\" indicates whether a protein is annotated as 
             having a signal peptide according to UniProt. \`\`VDM\" shows 
             whether a protein has previously been detected in vesicle-depleted 
             culture media (i.e. the proteins may also be in the soluble secretome) 
             (31). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in Supplementary Figure S1."

@@

# export table 1 LaTeX code with \\ line endings removed in a text file
tab1_clean <- gsub("\\\\\\\\\n", "\n", tab1)

cat(tab1_clean, file = "tables/table_1.txt", sep = "\n")

@@

# figure 4c MDS [dim1, dim2]
f4c <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(1,2)) + 
  scale_x_continuous(limits = c(-1.5, 2), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-2, 1.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical") + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 1") + 
  ylab(label = "Dimension 2")

# figure 4d MDS [dim3, dim2]
f4d <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(3,2)) + 
  scale_x_continuous(limits = c(-1.5, 2), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-2, 1.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical", 
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0.1), 
        legend.box.margin = margin(t = -10, r = -6, b = -10, l = -10)) + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 3") + 
  ylab(label = "Dimension 2")

>>>>

```{r table1}
tab1_cap <- "\\textbf{Candidate positive protein markers for 
             \\textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \\textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (48, 49) unless otherwise 
             indicated. The log\\textsubscript{2} ratio of the abundance 
             (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
             whole cell lysate (WCL) for each strain is listed. \`\`ex\" 
             indicates where a protein was only quantified in the EV fraction 
             and not the WCL for that strain. The \`\`TM\" column indicates the 
             number of transmembrane domains for each protein as annotated in 
             UniProt. \`\`SP\" indicates whether a protein is annotated as 
             having a signal peptide according to UniProt. \`\`VDM\" shows 
             whether a protein has previously been detected in vesicle-depleted 
             culture media (i.e. the proteins may also be in the soluble secretome) 
             (31). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in Supplementary Figure S1."

@@

# export table 1 LaTeX code (to be converted to docx with Pandoc)
cat(tab1, file = "tables/table_1.tex", sep = "\n")

@@

# figure 4c MDS [dim1, dim2]
f4c <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(1,2)) + 
  scale_x_continuous(limits = c(-1.5, 2), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-2, 1.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(1, 2, 3, 4)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical") + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 1") + 
  ylab(label = "Dimension 2")

# figure 4d MDS [dim3, dim2]
f4d <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(3,2)) + 
  scale_x_continuous(limits = c(-1.5, 2), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-2, 1.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(1, 2, 3, 4)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical", 
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0.1), 
        legend.box.margin = margin(t = -10, r = -6, b = -10, l = -10)) + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 3") + 
  ylab(label = "Dimension 2")

### 2020-03-30 inst/manuscript/tables/table_1.tex
Fix Figure 4C 4D colours
Also, fix minor typos.

\caption{\label{tab:}\textbf{Candidate positive protein markers for 

@@

             Database (candidagenome.org) (ref:footnote1) unless otherwise 

@@

\hspace{1em}\underline{ARF3} & \underline{Arf family GTPase<sup>a</sup>} & \underline{ex} & \underline{1.69} & \underline{ex} & \underline{3.45} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}ENA21 & Predicted P-type ATPase sodium pump<sup>a</sup> & ex & ex & ex & ex & 9 &  & \\
\hspace{1em}\underline{FAA4} & \underline{Long-chain fatty acid-CoA ligase<sup>a</sup>} & \underline{2.89} & \underline{2.24} & \underline{2.28} & \underline{1.45} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{EVP1<sup>d</sup>} & \underline{\textit{S. cerevisiae} ortholog is Pun1, plasma membrane protein<sup>a</sup>} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{3} & \underline{} & \underline{Y}\\

@@

\hspace{1em}\underline{SSO2} & \underline{Plasma membrane t-SNARE<sup>a</sup>} & \underline{ex} & \underline{1.88} & \underline{3.57} & \underline{ex} & \underline{1} & \underline{} & \underline{}\\
\hspace{1em}\underline{SUR7} & \underline{Protein required for normal cell wall, plasma membrane<sup>c</sup>} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{7.04} & \underline{4} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{orf19.1054} & \underline{\textit{S. cerevisiae} ortholog is Pom33, transmembrane nucleoporin<sup>b</sup>} & \underline{5.66} & \underline{ex} & \underline{ex} & \underline{2.51} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{orf19.2168.3} & \underline{\textit{S. cerevisiae} ortholog is Yop1, reticulon-interacting protein<sup>a</sup>} & \underline{4.77} & \underline{1.98} & \underline{2.29} & \underline{1.81} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{orf19.3799} & \underline{\textit{S. cerevisiae} ortholog is Rtn1, reticulon protein<sup>b</sup>} & \underline{2.24} & \underline{1.40} & \underline{3.00} & \underline{1.29} & \underline{2} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{SEC4} & \underline{Rab family GTPase<sup>a</sup>} & \underline{1.88} & \underline{1.20} & \underline{1.86} & \underline{2.90} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{YKT6} & \underline{Palmitoyltransferase, putative vacuolar SNARE complex protein<sup>a</sup>} & \underline{ex} & \underline{4.01} & \underline{5.46} & \underline{3.20} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{YPT31} & \underline{Rab family GTPase<sup>a</sup>} & \underline{ex} & \underline{1.57} & \underline{1.33} & \underline{3.33} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{VAC8} & \underline{Protein involved in vacuolar inheritance<sup>a</sup>} & \underline{2.79} & \underline{ex} & \underline{ex} & \underline{3.83} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}MIR1 & Putative mitochondrial phosphate transporter<sup>a</sup> & 3.68 & 4.38 & 4.24 & 1.60 &  &  & \\
\hspace{1em}POR1 & Mitochondrial outer membrane porin<sup>a</sup> & 3.44 & 2.51 & 3.69 & 1.38 &  &  & \\

>>>>

\caption{(\#tab:table1)\textbf{Candidate positive protein markers for 

@@

             Database (candidagenome.org) (48, 49) unless otherwise 

@@

\hspace{1em}\underline{ARF3} & \underline{Arf family GTPase\textsuperscript{a}} & \underline{ex} & \underline{1.69} & \underline{ex} & \underline{3.45} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}ENA21 & Predicted P-type ATPase sodium pump\textsuperscript{a} & ex & ex & ex & ex & 9 &  & \\
\hspace{1em}\underline{FAA4} & \underline{Long-chain fatty acid-CoA ligase\textsuperscript{a}} & \underline{2.89} & \underline{2.24} & \underline{2.28} & \underline{1.45} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{EVP1\textsuperscript{d}} & \underline{\textit{S. cerevisiae} ortholog is Pun1, plasma membrane protein\textsuperscript{a}} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{3} & \underline{} & \underline{Y}\\

@@

\hspace{1em}\underline{SSO2} & \underline{Plasma membrane t-SNARE\textsuperscript{a}} & \underline{ex} & \underline{1.88} & \underline{3.57} & \underline{ex} & \underline{1} & \underline{} & \underline{}\\
\hspace{1em}\underline{SUR7} & \underline{Protein required for normal cell wall, plasma membrane\textsuperscript{c}} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{7.04} & \underline{4} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{orf19.1054} & \underline{\textit{S. cerevisiae} ortholog is Pom33, transmembrane nucleoporin\textsuperscript{b}} & \underline{5.66} & \underline{ex} & \underline{ex} & \underline{2.51} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{orf19.2168.3} & \underline{\textit{S. cerevisiae} ortholog is Yop1, reticulon-interacting protein\textsuperscript{a}} & \underline{4.77} & \underline{1.98} & \underline{2.29} & \underline{1.81} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{orf19.3799} & \underline{\textit{S. cerevisiae} ortholog is Rtn1, reticulon protein\textsuperscript{b}} & \underline{2.24} & \underline{1.40} & \underline{3.00} & \underline{1.29} & \underline{2} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{SEC4} & \underline{Rab family GTPase\textsuperscript{a}} & \underline{1.88} & \underline{1.20} & \underline{1.86} & \underline{2.90} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{YKT6} & \underline{Palmitoyltransferase, putative vacuolar SNARE complex protein\textsuperscript{a}} & \underline{ex} & \underline{4.01} & \underline{5.46} & \underline{3.20} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{YPT31} & \underline{Rab family GTPase\textsuperscript{a}} & \underline{ex} & \underline{1.57} & \underline{1.33} & \underline{3.33} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}\underline{VAC8} & \underline{Protein involved in vacuolar inheritance\textsuperscript{a}} & \underline{2.79} & \underline{ex} & \underline{ex} & \underline{3.83} & \underline{} & \underline{} & \underline{}\\

@@

\hspace{1em}MIR1 & Putative mitochondrial phosphate transporter\textsuperscript{a} & 3.68 & 4.38 & 4.24 & 1.60 &  &  & \\
\hspace{1em}POR1 & Mitochondrial outer membrane porin\textsuperscript{a} & 3.44 & 2.51 & 3.69 & 1.38 &  &  & \\
